Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
RPM --> angular velocity
lbf --> pound-force

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a Kollmorgen \hl {AKM}
%please define AKM and RPM
  permanent magnet servo \hl {motor (Manufacturer, City, Country)} with a 20:1 gearbox,
providing precise control over shaft \hl {RPM}. This servo was controlled by the tow
tank's main motion controller for high synchronization with the carriage motion,
thereby giving precise measurement and control of the tip speed ratio. An Interface
T8 200-Nm capacity rotary torque \hl {transducer (Manufacturer, City, Country)} was installed inline between the
servo and the turbine, and the servo was also mounted on a slewing ring bearing,
which allowed a redundant measurement of torque via an arm and load cell used to
counteract the turbine moment. The frame was mounted to the carriage via linear
guides, such that the total streamwise drag force was transferred to a pair of
Sentran \hl {ZB3 500-lbf} %please define/check the unit
 capacity S-beam \hl {load cells (Manufacturer, City, Country)}, providing the rotor drag
measurements, after a separately measured tare drag was subtracted in post-processing. Similarly, a tare torque was measured by rotating the turbine shaft
in air. Turbine angular and tow carriage linear position were measured using
quadrature encoder signals, with $10^5$ counts-per-rev for the turbine and 10 ${\mu}$m resolution for the carriage position. These~signals, along with
the torque and drag signals, were sampled at 2 kHz.

>>>>

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a Kollmorgen \hl {AKM}
%please define AKM and RPM
  permanent magnet servo \hl {motor (Manufacturer, City, Country)} with a 20:1 gearbox,
providing precise control over shaft angular velocity. This servo was controlled by the tow
tank's main motion controller for high synchronization with the carriage motion,
thereby giving precise measurement and control of the tip speed ratio. An Interface
T8 200-Nm capacity rotary torque \hl {transducer (Manufacturer, City, Country)} was installed inline between the
servo and the turbine, and the servo was also mounted on a slewing ring bearing,
which allowed a redundant measurement of torque via an arm and load cell used to
counteract the turbine moment. The frame was mounted to the carriage via linear
guides, such that the total streamwise drag force was transferred to a pair of
Sentran ZB3 500 pound-force
 capacity S-beam \hl {load cells (Manufacturer, City, Country)}, providing the rotor drag
measurements, after a separately measured tare drag was subtracted in post-processing. Similarly, a tare torque was measured by rotating the turbine shaft
in air. Turbine angular and tow carriage linear position were measured using
quadrature encoder signals, with $10^5$ counts-per-rev for the turbine and 10 ${\mu}$m resolution for the carriage position. These~signals, along with
the torque and drag signals, were sampled at 2 kHz.
